### 2016-05-19 2016-lrec-tyvmorph/poster.tex
more hargling
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@68626 72bbbca6-d526-0410-a7d9-f06f51895060

%\usepackage{natbib}
\usepackage[backend=biber,citestyle=apa,maxcitenames=2,style=authoryear,maxbibnames=99,uniquelist=false,uniquename=false]{biblatex}
\bibliography{poster}
\renewcommand*{\nameyeardelim}{\addcomma\space}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\intitlepunct}{\space}

@@

		\headerbox{Development cycle}{name=development,below=morphtrans,span=1}{
		\centering
		\begin{tikzpicture}[xscale=1.45,yscale=2.2]%, auto]

@@

	\headerbox{Evaluation}{name=results,column=2,below=example}{ %lexicon}{
		\begin{multicols}{2}	
		\begin{tabular}{lrr}
			\toprule
				& precision & recall \\
			\midrule
			known & 0.99 & 0.97 \\
			all & 0.99 & 0.69 \\
			\bottomrule
		\end{tabular}\\
		{\qipa ↑} quantitative eval\\
		\newline
		\vspace{0.01pt}\hfill{}qualitative eval {\qipa ↗}\\
		\columnbreak
		\begin{tabular}{lr}
			\toprule
			error type & count \\
			\midrule
			Missing stem & 364 \\
			Other & 65 \\
			Morphotactics & 19 \\
			Phonology & 8 \\
			Categorisation & 6 \\
			\bottomrule
		\end{tabular}
		\end{multicols}
		%\vspace{0.05em}

@@

		\headerbox{Ongoing and future work}{name=nedostatki,column=1,below=example}{
		\htwo{our other Turkic-language transducers}
		\begin{itemize}
			%\item Turkish (\hiliteone{Çöltekin, 2010 \& 2014}; \hilitetwo{Oflazer, 1994})
			%\item Crimean Tatar (\hilitetwo{Altıntaş, 2001})
			%\item Turkmen (\hilitetwo{Tantuğ et al., 2006})
			%\item Kazakh (\hilitetwo{Бекманова \& Махимов, 2013})
			%\vspace{1pt}\hfill{} \hiliteone{GPL (=free and open)}!
			%\item our Kyrgyz, Kazakh, Tatar, Kumyk:\ all \hiliteone{GPL (=free and open)}!
			\item \textbf{Kyrgyz} \parencite{jnwmifmt2012lrecpaper}%  (Washington et al., 2012)
			\item \textbf{Tatar} \& \textbf{Bashkort} \parencite{fmtjnwisrb2012lrecpaper} %(Tyers et al., 2012)
			\item \textbf{Kazakh} \parencite{isjnwfmt2013mtsummitpaper} %(Salimzyanov et al., 2013)
			\item \textbf{Kumyk} \parencite{jnwisfmt2014lrecpaper} %(Washington et al., 2014)
			\item ongoing work on Sakha, Khakas, and more!
		\end{itemize}
		\dividerspace{}

>>>>

%\usepackage{natbib}
\usepackage[backend=biber,citestyle=apa,maxcitenames=2,style=authoryear,maxbibnames=99,uniquelist=false,uniquename=false]{biblatex}
\bibliography{poster}
\renewcommand*{\nameyeardelim}{\addcomma\space}
\renewcommand*{\bibfont}{\scriptsize}
\renewcommand*{\intitlepunct}{\space}

@@

	\headerbox{What should we put here}{name=harglebargle,column=0,below=morphtrans}{
		\vspace{0.5in}

		\headerbox{Development cycle}{name=development,below=harglebargle,span=1}{
		\centering
		\begin{tikzpicture}[xscale=1.45,yscale=2.6]%, auto]

@@

	\headerbox{Evaluation}{name=results,column=2,below=example}{ %lexicon}{
		%\begin{multicols}{2}	
		\begin{itemize}
			\item Naïve coverage calculated on 5-part corpus
		\end{itemize}
		\begin{center}
		\resizebox{0.9\textwidth}{!}{
		\begin{tabular}{lrr}
			\toprule
			 \textbf{Domain} & \textbf{Tokens} & \textbf{Coverage} (\%) \\
			\midrule
			 News       & 1,539,459 &  95.73  \\
			 Religion   & 746,124 &  93.84 \\
			 Literature & 297,830 &  91.96  \\
			 Encyclopaedic  & 276,547 & 90.86 \\
			 Folklore & 27,902 & 91.57  \\\cline{2-3}
			 Average    & -- & 92.79 \\
			\bottomrule
		\end{tabular}}
		\end{center}

		\begin{itemize}
			\item Good results reflect high accuracy
		\end{itemize}
		\begin{center}
		\resizebox{0.9\textwidth}{!}{
		\begin{tabular}{llrr}
			\toprule
				& \textbf{count} & \textbf{precision} & \textbf{recall} \\
			\midrule
			known tokens & 1024 & 0.99 & 0.97 \\
			all tokens & 1425 & 0.99 & 0.69 \\
			\bottomrule
		\end{tabular}}
		\end{center}
		%{\qipa ↑} quantitative eval\\
		%\newline
		%\vspace{0.01pt}\hfill{}qualitative eval {\qipa ↗}\\
		%\columnbreak
		\begin{itemize}
			\item Qualitative evaluation
		\end{itemize}

		\begin{center}
		\resizebox{0.9\textwidth}{!}{
		\begin{tabular}{lrr}
			\toprule
			\textbf{error type} & \textbf{count} & \textbf{percentage} \\
			\midrule
			Missing stem &  364 & 78.8 \\
			Other & 65 & 14.1  \\
			Bad morphotactics & 19 & 4.1  \\
			Bad phonology & 8 & 1.7  \\
			Incorrect categorisation & 6 & 1.3  \\
			\midrule
			Total: & 462 & 100 \\
			\bottomrule
		\end{tabular}}
		\end{center}

	%	\begin{tabular}{lr}
	%		\toprule
	%		error type & count \\
	%		\midrule
	%		Missing stem & 364 \\
	%		Other & 65 \\
	%		Bad morphotactics & 19 \\
	%		Bad phonology & 8 \\
	%		Incorrect categorisation & 6 \\
	%		\bottomrule
	%	\end{tabular}
		%\end{multicols}
		%\vspace{0.05em}

@@

		\headerbox{Morphotactics}{name=morphotactics,column=1,below=example}{
			\centering
			\includegraphics[width=0.9\textwidth]{img/dibuix}

		\headerbox{Ongoing and future work}{name=nedostatki,column=1,below=morphotactics}{
		\htwo{our other Turkic-language transducers}
		\begin{itemize}
			%\item Turkish (\hiliteone{Çöltekin, 2010 \& 2014}; \hilitetwo{Oflazer, 1994})
			%\item Crimean Tatar (\hilitetwo{Altıntaş, 2001})
			%\item Turkmen (\hilitetwo{Tantuğ et al., 2006})
			%\item Kazakh (\hilitetwo{Бекманова \& Махимов, 2013})
			%\vspace{1pt}\hfill{} \hiliteone{GPL (=free and open)}!
			%\item our Kyrgyz, Kazakh, Tatar, Kumyk:\ all \hiliteone{GPL (=free and open)}!
			\item \textbf{Kyrgyz} \parencite{jnwmifmt2012lrecpaper}%  (Washington et al., 2012)
			\item \textbf{Tatar} \& \textbf{Bashkort} \parencite{fmtjnwisrb2012lrecpaper} %(Tyers et al., 2012)
			\item \textbf{Kazakh} \parencite{isjnwfmt2013mtsummitpaper} %(Salimzyanov et al., 2013)
			\item \textbf{Kumyk} \parencite{jnwisfmt2014lrecpaper} %(Washington et al., 2014)
			\item ongoing work on Sakha, Khakas, and more!
		\end{itemize}
		\dividerspace{}
